IAPS_Preprocessing

### 2022-02-07 Old scripts/IAPS_PREPROCESSING.Rmd
07 Jan return

---
title: "Preprocing and mergind datasets"
author: "Helio Cuve"
date: "24/01/2020"
output:
  word_document: default
  html_document: default
---

# Loading rdhf5 
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.10")

BiocManager::install("rhdf5")
library(rhdf5)

# Preferences
list necessary package install them if not already and load them
```{r}
# devtools::install_github("dmirman/gazer")

list.of.packages <- c("ggplot2", "data.table", 'readr', "c", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
# lapply(new.packages, require, character.only = TRUE)

# install.packages('devtools')

remotes::install_github("dmirman/gazer")
library(gazer)
library(dplyr)

# setting a workspace

#change approproatelly

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
# hdf5FilesPath<- "~/Desktop/University Work/Research_Project/Data Analysis January 2020/Data Analysis Jan 2020"
setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
hdf5FilesPath<- "D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020"

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")

# 2021 data
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

@@

# gp extractor function
takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff

Starting from 322 we have gsr v and hr v. and Pulse is around the 30

```{r, gp extractor}
gp.extractor(hdf5FilesPath)

gp.extractor = function(hdf5FilesPath) {

@@

    return(message('No HDF5 files found in the directory provided.'))
  }
   # f = 7
  for (f in 1:length(hdfFilesList)) {

@@

    #notr this sometimes fails because e are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    # Fixing 228
    # session 1 = IAPS
    nrow(tmp.events)
    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)

@@

Problem files
```{r}
# 355  - did not finish IAPS
# adjust below manually

gp.extractor = function(hdf5FilesPath) {

  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
  hdfFilesList
  if (length(hdfFilesList) == 0){

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 10# adjust here to the index for the probematic file
  for (f in 1:length(hdfFilesList)) {

    #ATTTENTIONNN  note this sometimes fails because we are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    # Fixing 228
    # session 1 = IAPS
    nrow(tmp.events)
    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)

    unique(tmp.events$screencontent)

    # tmp.eyetr_backup<- tmp.eyetr
    # tmp.df_backup<- tmp.df
    # tmp.df<- tmp.df_backup
    colnames(tmp.df)
    # rm(tmp.raw.trial)
    # colnames(tmp.raw.trial)
    colnames(tmp.df)
    colnames(tmp.events1)
    colnames(tmp.eyetr)
    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    # e=10
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
    message(sprintf("subsetting eyetracking data"))
    e=1
    for(e in 1:nrow(tmp.events1)) {

# tmp_full<- gp.extractor(hdf5FilesPath)

# for some reason 355 is creating duplicate event ids
library(readr)
ss355_GPdata_ <- read_csv("ss355_GPdata .csv")

View(ss355_GPdata_)

ss355_GPdata_nodup <- subset(ss355_GPdata_, !duplicated(ss355_GPdata_$event_id))

write_csv(ss355_GPdata_nodup, "ss355_GPdata_nodup.csv")

now cleaning
we need to have data for ledalab
gaze path
clean and trackloss

```{r, cleaning}
# function to read all the csvs into one dataframe

rm(tmp_full)
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# now read them
# setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/step1")

tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))
# rm(db_beh)

tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)

unique(tmp.df2$ssid)
head(tmp.df2)

@@

  # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
  message(sprintf("step 4 cuting off screen in points and repixel"))
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

@@

```{r}
library(tidyverse)
colnames(tmp.df2)
tmp.df3<- tmp.df2

# tmp.df3<- tmp.df2
colnames(tmp.df3)

@@

head(tmp.df3)

# make zeros
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)

# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(Condition, tNo, ssid)%>%
  # group_by(text)%>%
  fill(zero)

unique(tmp.df3$zero)

# rezero
tmp.df3<-tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)

natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

# let's check to see if it looks fine - NOTE THIS IS a bit SLOW
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

@@

    # fill down
tmp.df3<- tmp.df3%>%
      # arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim)

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))

tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

# let's check
unique(tmp.df3$ssid)

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
tmp.df3%>%
subset(Condition == 'IAPS' & ssid ==  353)%>%
  ggplot(aes(x = timerezero3, y= gsr))+
  stat_smooth()+
    # geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

tmp.df3%>%
subset( tNo == -5)%>%
  ggplot( aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

triggers

```{r}
unique(tmp.df3$tNo)

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)

tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                  NULL))

# takes a bit with a group - so don't run
# ggplot(tmp.df3, aes(time, gsr))+
#   geom_line()+
#   geom_vline(aes(xintercept = intercept_time))

# should trigger be this or should I create a unique code for this based on the images

unique(tmp.df3$tNo)

@@

tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
unique(tmp.df3$trigger)

tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))

tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)

@@

```{r}

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

options(scipen = 999)

tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

unique(db_GSR$Condition)

@@

    for (ssid in names(split_gsr)) {
      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
    }

# baselining gsr
```{r}
# use ms to baseline
tmp.df3_backup<- tmp.df3

@@

# create baseline median
tmp.df3$gsr_bas_mean<- NULL

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

# fill the baseline mean
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median)

# fill up to complete
unique(tmp.df3$gsrv)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median, .direction = 'up')

# do baseline correction
# 
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(gsr_basCor = gsr_ms - gsr_bas_median)

# rest baselining
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition)%>%
  mutate(gsr_restmedian = median(gsr_ms))

tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)

@@

tmp.df3_backup<- tmp.df3
# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response =   max(gsr_basCor))

# gsr response for every bit
unique(tmp.df3$screencontent)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

unique(tmp.df3$gsr_response )

tmp.df3_backup<- tmp.df3
```

@@

min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)

tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)

tmp.df3_backup <- tmp.df3

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, trialUnq,tNo, time)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

@@

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
# ?smooth_interpolate_pupil

# library(gazer)

?smooth_interpolate_pupil

# vert order dependent
tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<- tmp.df3 %>%
#   group_by(ssid, trialUnq,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=10, 
#                                     filter = 'moving',
#                                     type="linear", hz=20, n = 10)
# 
# 
# tmp.df3<-
#   tmp.df3%>%
#   arrange(ssid,tNo,time)
#   # group_by(ssid, tNo, timerezero3)%>%
# 
# tmp.df3te<- tmp.df3 %>%
#   group_by(ssid, Condition,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=Inf, 
#                                     filter = 'moving',
#                                     type="linear", hz=100, n = 5)

min(tmp.df3$pup_interp, na.rm = TRUE)
max(tmp.df3$pup_interp, na.rm = TRUE)

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

# create baseline pupil mean
```{r}
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, pup_bastrue)%>%
  mutate(pup_bas_med = median(pup_bas))

# fill the baseline mean pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid,tNo)%>%
  fill(pup_bas_med)

# fill up to complete pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(pup_bas_med, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo, time)%>% # pay attentipn to order
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

@@

# MAD removal
library(gazer)
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

tmp.df3<- max_pup

# instead of deleting, nus put NA
tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
```
unique(tmp.df3$ssid)

>>>>

---
title: "IAPS_Preprocessing"
author: '@H Cuve'
date: "12/12/2019"
output: html_document
---

# Preferences
list necessary package install them if not already and load them
```{r eval=FALSE, include=FALSE}
# devtools::install_github("dmirman/gazer")

list.of.packages <- c("ggplot2", "data.table", 'readr', "rhdf5", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
lapply(new.packages, require, character.only = TRUE)

# setwd("~/Documents/Intero Study/data/Bio/Dec12")
hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

@@

# gp extractor fucntion
takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff

```{r, gp extractor}
gp.extractor(hdf5FilesPath)
gp.extractor = function(hdf5FilesPath) {

@@

    return(message('No HDF5 files found in the directory provided.'))
  }
  # f = 1
  for (f in 1:length(hdfFilesList)) {

@@

    #notr this sometimes fails because e are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')
    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

@@

now cleaning
we need to have data for ledalab
gaze path
clean and tracloss

```{r, cleaning}
# function to read all the csvs into one dataframe
rm(tmp_full)
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", 'hr',"status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# now read them

tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))
rm(db_beh)

tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)
unique(tmp.df2$ssid)
head(tmp.df2)

@@

  # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
  message(sprintf("step 4 cutingt off screen in points and repixel"))
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

@@

```{r}
colnames(tmp.df2)
tmp.df3<- tmp.df2
# tmp.df3<- tmp.df2
colnames(tmp.df3)

@@

# make zeros
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)
# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(Condition, tNo, ssid)%>%
  # group_by(text)%>%
  fill(zero)
# rezero
tmp.df3<-tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
# let's check to see if it looks fine
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

# ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS'), aes(timerezero, gsr, colour = as.factor(ssid)))+
#   geom_line()

@@

    tmp.df3<- tmp.df3%>%
      # arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim)

   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))
   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

# let's check
unique(tmp.df3$ssid)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -1) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

triggers
```{r}
unique(tmp.df3$tNo)
natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

tmp.df3$intercept_time<- if_else
(tmp.df3$firststart == FALSE, tmp.df3$time, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                  NULL))
# takes a bit with a group - so don't run
ggplot(tmp.df3, aes(time, gsr))+
  geom_line()+
  geom_vline(aes(xintercept = intercept_time))

# should trigger be this or should I create a uoque code for this based on the images
unique(tmp.df3$tNo)

@@

tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))

unique(tmp.df3$trigger)
tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)

@@

```{r}
tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000
options(scipen = 999)
tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  17, 47, 46 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

@@

    for (ssid in names(split_gsr)) {
      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
    }
```

# baselining gsr
```{r}
# use ms to baseline

@@

# create bseline median
tmp.df3<- tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_mean = median(gsr_bas))

# fill the baseline mean
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_mean)

# fill up to complete
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_mean, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(gsr_basCor = gsr_ms - gsr_bas_mean)

# rest baselining
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition)%>%
  mutate(gsr_restmean = median(gsr_ms))

tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmean, tmp.df3$gsr_basCor)

@@

@@

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)
min(tmp.df3$pupil, na.rm = TRUE)

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq) %>%
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == -3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

@@

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
?smooth_interpolate_pupil

library(gazer)
tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<-test

min(tmp.df3$pup_interp)
max(tmp.df3$pup_interp)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4 & tmp.df3$ssid == 309) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~Condition)

# create baseline pupil mean
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(tNo, pup_bastrue)%>%
  mutate(pup_bas_med = median(pup_bas))

# fill the baseline mean pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(tNo)%>%
  fill(pup_bas_med)

# fill up to complete pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(tNo)%>%
  fill(pup_bas_med, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  # arranÇge(time)%>%
  group_by(tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

@@

# MAD removal
tmp.df3<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))%>%
  dplyr::filter(speed < MAD)

tmp.df3

ggplot(subset(tmp.df3, tmp.df3$tNo == -3), aes(x = timerezero3, y = pup_basCor, colour = as.factor(ssid)))+
  geom_line()

ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = F)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

unique(tmp.df3$ssid)
